Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-11-18 src/tex/ms.tex
fixing axes stuff and discussion

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the entire population for each model in grey. Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

We \textbf{highlight} that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, the number of resolved sources is not reduced to an equal degree. This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved. For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by \textbf{$\sim 17$\%} and increased by \textbf{$\sim3\%$} respectively\textbf{, with relatively unchanged overall LISA population sizes}. For $\alpha5$ the number of resolvable DWDs is reduced by only \textbf{$\sim 22\%$}, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a \textbf{$\sim 5\%$} reduction even though the overall LISA population of both variations is halved. \textbf{The majority of systems which become resolvable with a lower foreground (in model FZ) are non-chirping systems. This is because both chirping and non-chirping systems have their populations halved, but the lower foreground allows a relative increase in the number of resolved non-chirping sources. Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$. The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}

@@

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This is illustrated in Figure \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two. This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model.

@@

The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of \textbf{two} for model FZ relative to model F50 for variations $\alpha5$ and $q3$, however the number of resolved\textbf{, i.e. observable,} sources is not reduced to an equal degree. The number of observable systems with SNR $>7$ increases by 3\% for $\alpha25$\textbf{, mimicking the LISA-band population remaining relatively unchanged}. \textbf{However, }the number of \textbf{observable} DWDs is reduced by only 26\% for $\alpha5$, and \textbf{by only 1\% for $q3$}, even though the overall LISA population of both variations is halved. \textbf{Maintaining} the number of DWDs in parameter variation $q3$ is contributed to \textbf{largely} by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).

>>>>

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the the entire population for each model in grey. Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

@@

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This is illustrated in Figure \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two. This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model. \textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree. This is because an absence of fewer competing GW signals from DWDs in the LISA frequency band leads to individually resolved DWDs. See Appendix \ref{appendix:ASD_vars} for more details.}

@@

\textbf{The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ affects the number of resolvable systems in each parameter variation. For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by $\sim 17$\% and increased by $\sim3\%$ respectively, with relatively unchanged overall LISA population sizes. For $\alpha5$ the number of resolvable DWDs is reduced by only $\sim 22\%$, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a $\sim 5\%$ reduction even though the overall LISA population of both variations is halved. The majority of systems which become resolvable with a lower foreground (in model FZ) are non-chirping systems. This is because both chirping and non-chirping systems have their populations halved, but the lower foreground allows a relative increase in the number of resolved non-chirping sources. Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$. The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}
